R Notebook

### 2023-06-05 Scripts/data_cleaning.Rmd
Updates to text + section on Cox models

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% dplyr::rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(protests = nelda9)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(opp.votegain = nelda7)
nelda <- nelda %>% rename(nelda.protests.fraud = nelda30)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)
nelda <- nelda %>% rename(preelection_concerns = nelda11)
nelda <- nelda %>% rename(harass_opp = nelda15)
nelda <- nelda %>% rename(opp_leaders_prevented = nelda13)

@@

@@

@@

Note: the missing values from NELDA are cases not included in VDEM (e.g. Bahamas, Dominica.)
```{r}
nelda <- nelda %>% mutate(country_id = countrycode(sourcevar = ccode, origin = "gwn", destination = "vdem"))
 #Missing matches here look to be countries below the population threshold: some Carib. islands, Monaco, etc.
lji <- lji %>% mutate(country_id = countrycode(sourcevar = ccode, origin = "cown", 
                                               destination = "vdem"))

@@

ecav <- ecav %>% mutate(country_id = countrycode(sourcevar = ccode, origin = "cown", destination = "vdem"))

@@

```{r}
vdem.recent <- vdem.data %>% filter(year >= 1944)

@@

vdem.recent <- vdem.recent %>% group_by(country_id) %>% mutate(v2elirreg.inv.lag = lag(v2elirreg.inv))

@@

@@

nelda2 <- nelda2 %>% merge(vdem.recent %>% dplyr::select(v2elintmon.lag, v2elintmon, v2eltvrexo, v2elvotlrg, v2elvotsml, v2ellostlg, v2ellostsl, v2ellostsm, v2ellostss, v2ellovtlg, v2ellovtsm, v2x_polyarchy, v2x_libdem, v2x_partipdem, v2x_delibdem, v2x_egaldem, v2x_freexp_altinf, v2x_api, v2x_mpi, v2x_frassoc_thick, v2x_suffr, v2xel_frefair, v2x_elecoff, v2x_liberal, v2x_jucon, v2x_partip, v2x_cspart, v2xeg_eqdr, v2psoppaut, v2jureform, v2jupurge, v2jupoatck, v2jupack, v2juaccnt, v2juhcind, v2juncind, v2mecenefm, e_migdppcln, e_migdpgro, e_miinflat, v2xlg_legcon, legcon.1lag, polyarchy.1lag, libdem.1lag, partipdem.1lag, 

@@

@@

```{r}
urban <- read.csv(here::here("Data", "urbanization_worldbank.csv"))
test <- urban %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "year")
test <- test %>% mutate(year = gsub("X", "", year))

@@

test <- test %>% mutate(stateid = countrycode(sourcevar = Country.Code, origin = 'iso3c', destination = 'gwc'))
test <- test %>% rename(urban.pct = value)
test <- test %>% dplyr::select(year, urban.pct, stateid)

nelda2 <- nelda2 %>% mutate(year = as.character(year))

nelda2 <- nelda2 %>% left_join(test, by = c("stateid", "year"))

@@

@@

## Violence
violence_data_post <- ecav.post %>% group_by(NeldaID) %>% summarize(antigov.violence = sum(antigov.violence, na.rm = T))
violence_data_pre <- ecav.pre %>% group_by(NeldaID) %>% summarize(antigov.violence.pre = sum(antigov.violence, na.rm = T))

##Combined
ecav_data_post <- left_join(count_data_post, duration_data, by = "NeldaID")
ecav_data_post <- left_join(ecav_data_post, size_data_post, by = "NeldaID")
ecav_data_post <- left_join(ecav_data_post, violence_data_post, by = "NeldaID")

ecav_data_pre <- left_join(count_data_pre, size_data_pre, by = "NeldaID")
ecav_data_pre <- left_join(ecav_data_pre, violence_data_pre, by = "NeldaID")

@@

```{r}
nelda2.sub <- nelda2 %>% filter(v2x_regime == 1 | v2x_regime == 2) #Note that coding scheme for electoral democracies allows for "some degree of fraud and irregularities but these did not in the end affect the outcome" (v2elfrfair, which is a component of v2x_regime) 
```

@@

```{r}
nelda2.sub <- nelda2.sub %>% filter(election_mdy >= "1989-10-04")
nelda2.test <- nelda2.sub %>% filter(election_mdy <= "2013-01-13")
```

@@

nelda2.sub <- nelda2.sub %>% mutate(antigov.violence = ifelse(is.na(antigov.violence)==T, 0, antigov.violence))
nelda2.sub <- nelda2.sub %>% mutate(n.events.post = ifelse(is.na(n.events.post)==T, 0, n.events.post))
nelda2.sub <- nelda2.sub %>% mutate(d.events.num = ifelse(is.na(d.events.num)==T, 0, d.events.num))
#nelda2.sub <- nelda2.sub %>% mutate(median.participants = ifelse(is.na(median.participants)==T, 0, median.participants))

@@

##Making the assumption that NAs for pre-election protest are zero
nelda2.sub <- nelda2.sub %>% mutate(n.events.pre = ifelse(is.na(n.events.pre) == T, 0, n.events.pre))
nelda2.sub <- nelda2.sub %>% mutate(antigov.violence.pre = ifelse(is.na(antigov.violence.pre) == T, 0, antigov.violence.pre))

@@

nelda2.sub <- nelda2.sub %>% mutate(n.events.post = ifelse(is.na(n.events.post) == T, 0, n.events.post))
nelda2.sub <- nelda2.sub %>% mutate(antigov.violence = ifelse(is.na(antigov.violence) == T, 0, antigov.violence))

@@

 - Quick growth after fraud indicates opp believes state is weak
 - Slow or no growth after fraud indicates opp believes state is strong
 - Quick decay after peak indicates state is strong / believed strong
 - Slow decay after peak indicates state is weak / believed weak

@@

## Set up holding df

dv_df <- data.frame(NeldaID = NA, prot_intensity = NA, decay_intensity = NA)

## Replace categorical with min value, replace -99s

#ecav_rus <- ecav %>% filter(country == "Russia")   # Filter by country
ecav <- ecav %>% mutate(ParticipantNumber_num_min = ifelse(ParticipantNumber == 1, 2, 
                                ifelse(ParticipantNumber == 2, 10, 
                                       ifelse(ParticipantNumber == 3, 100, 
                                              ifelse(ParticipantNumber == 4, 1000,
                                                     ifelse(ParticipantNumber == 5, 10000, 10)))))) #Last 10 here hard-codes any missing participant size as 10

@@

 election_ids <- unique(ecav$NeldaID)

 for(i in 1:length(election_ids)){
 ecav_temp <- ecav %>% filter(NeldaID == election_ids[i])  #There is a loop here

@@

 ecav_temp_comb <- ecav_temp_comb %>% filter(date_col >= election_date_temp)
  if (nrow(ecav_temp_comb) == 0) {
    new_row <- data.frame(election_ids[i], NA, NA)
    dv_df[i,] <- new_row
    print(paste0("No post-election protests for obseveration ", i, ", election ID", election_ids[i], ","))
    next}  #End loop if zero post-election protests

@@

  if (nrow(max_data) > 1) {
    prot_intensity <- max_data$total[1] / (1 + as.numeric(ymd(max_data$date_col[1]) - ymd(election_date_temp))) #[1] gets the first peak
    last_peak <- tail(max_data, n = 1)
    decay_intensity <-  last_peak$total / (1 + as.numeric(max(ecav_temp_comb$date_col) - (ymd(last_peak$date_col))))
    new_row <- data.frame(election_ids[i], prot_intensity, decay_intensity)
  #new_row <- new_row %>% rename(NeldaID = election_ids.i.)
    dv_df[i,] <- new_row
    print(paste0("Election observation ", i, " completed. (Note: multiple peaks."))
    next
  }

@@

  new_row <- data.frame(election_ids[i], prot_intensity, decay_intensity)
  #new_row <- new_row %>% rename(NeldaID = election_ids.i.)
  dv_df[i,] <- new_row
  print(paste0("Election observation ", i, " completed."))

@@

@@

@@

```{r}
write.csv(nelda2.sub, here::here("Data", "nelda2_sub_2023-04-19.csv"))
```

>>>>

Cleaning nelda variables--this will have to be done for all used variables
```{r}
nelda <- nelda %>% dplyr::rename(first.mp.election = nelda2)
nelda <- nelda %>% rename(protests = nelda9)
nelda <- nelda %>% rename(inc.fav.cancel = nelda34)
nelda <- nelda %>% rename(inc.lose = nelda24)
nelda <- nelda %>% rename(inc.termlimit = nelda8)
nelda <- nelda %>% rename(econ.crisis.nelda = nelda18)
nelda <- nelda %>% rename(opp.votegain = nelda7)
nelda <- nelda %>% rename(nelda.protests.fraud = nelda30)
nelda <- nelda %>% rename(new.elections.held = nelda37)
nelda <- nelda %>% rename(inc.replaced.prot = nelda41)
nelda <- nelda %>% rename(preelection_concerns = nelda11)
nelda <- nelda %>% rename(harass_opp = nelda15)
nelda <- nelda %>% rename(opp_leaders_prevented = nelda13)
nelda <- nelda %>% rename(unscheduled_election = nelda6)
nelda <- nelda %>% rename(inc.run = nelda21)
nelda <- nelda %>% rename(chosen.successor = nelda22)

@@

nelda <- nelda %>% mutate(unscheduled_election = ifelse(is.na(unscheduled_election)==T, NA, ifelse(unscheduled_election == "yes" | unscheduled_election == "N/A", 1, 0)))   #"N/A" here refers to no common expectation for election timing

@@

nelda <- nelda %>% mutate(chosen.successor = ifelse(inc.run == "no" & chosen.successor == "yes", 1, 0))

@@

Note: the missing values from NELDA are cases not included in VDEM (e.g. Bahamas, Dominica.)
```{r}
nelda <- nelda %>% mutate(country_id = countrycode(sourcevar = ccode, origin = "gwn", destination = "vdem", 
                                                   custom_match = c("345" = "198"))) #Fixes Serbia; only non-match that needs fixing; others are microstates / not in V-Dem
 #Missing matches here look to be countries below the population threshold: some Carib. islands, Monaco, etc.
lji <- lji %>% mutate(country_id = countrycode(sourcevar = ccode, origin = "cown", 
                                               destination = "vdem",
                                               custom_match = c("345" = "198"))) #ID code is the same as above

@@

ecav <- ecav %>% mutate(country_id = countrycode(sourcevar = ccode, origin = "cown", destination = "vdem",
                                                 custom_match = c("345" = "198")))

@@

```{r, warning=FALSE}
vdem.recent <- vdem.data %>% filter(year >= 1944)

@@

@@

## Getting lagged election fraud
countryids <- data.frame(unique(vdem.recent$country_id))
lag_with_ids <- data.frame(country_id_year = NA, v2elirreg.inv.lag = NA)

for (i in 1:nrow(countryids)){
  #lag_with_ids <- data.frame(country_id_year = NA, v2elirreg.inv.lag = NA)
  country <- vdem.recent %>% filter(country_id == countryids[i,1])
  country <- country %>% filter(is.na(v2elirreg.inv) == F)
  country <- country %>% mutate(v2elirreg.inv.lag = lag(v2elirreg.inv))
  lag_with_ids_temp <- country %>% dplyr::select(country_id_year, v2elirreg.inv.lag)
  lag_with_ids <- bind_rows(lag_with_ids, lag_with_ids_temp)
}
lag_with_ids <- lag_with_ids %>% dplyr::select(-COWcode)
vdem.recent <- vdem.recent %>% left_join(lag_with_ids, by = "country_id_year")

@@

nelda2 <- nelda2 %>% merge(vdem.recent %>% dplyr::select(v2elintmon.lag, v2elintmon, v2eltvrexo, v2elvotlrg, v2elvotsml, v2ellostlg, v2ellostsl, v2ellostsm, v2ellostss, v2ellovtlg, v2ellovtsm, v2x_polyarchy, v2x_libdem, v2x_partipdem, v2x_delibdem, v2x_egaldem, v2x_freexp_altinf, v2x_api, v2x_mpi, v2x_frassoc_thick, v2x_suffr, v2xel_frefair, v2x_elecoff, v2x_liberal, v2x_jucon, v2x_partip, v2x_cspart, v2xeg_eqdr, v2psoppaut, v2jureform, v2jupurge, v2jupoatck, v2jupack, v2juaccnt, v2juhcind, v2juncind, v2mecenefm, e_migdppcln, e_migdpgro, e_miinflat, v2xlg_legcon, legcon.1lag, polyarchy.1lag, libdem.1lag, partipdem.1lag, v2elirreg.inv.lag,

@@

                                                  e_regionpol,

@@

```{r}
urban <- read.csv(here::here("Data", "urbanization_worldbank.csv"))
#urban <- urban %>% rename(Country.Name = X...Country.Name)
test <- urban %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "year")
test <- test %>% mutate(year = gsub("X", "", year))

@@

test <- test %>% mutate(stateid = countrycode(sourcevar = Country.Code, origin = 'iso3c', destination = 'gwc'))
test <- test %>% rename(urban.pct = value)

test <- test %>% mutate(country_id = countrycode(sourcevar = Country.Code, origin = 'iso3c', destination = 'vdem'))
test <- test %>% mutate(country_id_year = paste0(country_id, "_", year))

test <- test %>% dplyr::select(country_id_year, urban.pct)

nelda2 <- nelda2 %>% left_join(test, by = "country_id_year")

@@

Coding pro-gov violence from ecav

```{r}
## Coding pro-government initiation of violence

ecav <- ecav %>% mutate(progov.violence = 
                          ifelse(EventViolence == 0, 0,
                                 ifelse(ViolenceInitiator == "-99", NA,
                                                  ifelse(ViolenceInitiator == ".1" & Actor1Side == 0, 1, 
                                                  ifelse(ViolenceInitiator == ".2" & Actor2Side == 0, 1,
                                                         ifelse(ViolenceInitiator == "1.1" & Target1Side == 0, 1,
                                                                ifelse(ViolenceInitiator == "2.1" & Target2Side == 0, 1, 0)))))))
```

@@

## Anti-gov Violence
violence_data_post <- ecav.post %>% group_by(NeldaID) %>% summarize(antigov.violence = sum(antigov.violence, na.rm = T))
violence_data_pre <- ecav.pre %>% group_by(NeldaID) %>% summarize(antigov.violence.pre = sum(antigov.violence, na.rm = T))

## Pro-gov Violence
pg_violence_data_post <- ecav.post %>% group_by(NeldaID) %>% summarize(progov.violence = sum(progov.violence, na.rm = T))
pg_violence_data_pre <- ecav.pre %>% group_by(NeldaID) %>% summarize(progov.violence.pre = sum(progov.violence, na.rm = T))

##Combined
ecav_data_post <- left_join(count_data_post, duration_data, by = "NeldaID")
ecav_data_post <- left_join(ecav_data_post, size_data_post, by = "NeldaID")
ecav_data_post <- left_join(ecav_data_post, violence_data_post, by = "NeldaID")
ecav_data_post <- left_join(ecav_data_post, pg_violence_data_post, by = "NeldaID")

ecav_data_pre <- left_join(count_data_pre, size_data_pre, by = "NeldaID")
ecav_data_pre <- left_join(ecav_data_pre, violence_data_pre, by = "NeldaID")
ecav_data_pre <- left_join(ecav_data_pre, pg_violence_data_pre, by = "NeldaID")

@@

```{r}
nelda2.sub <- nelda2 %>% filter(v2x_regime > 0) #Note that coding scheme for electoral democracies allows for "some degree of fraud and irregularities but these did not in the end affect the outcome" (v2elfrfair, which is a component of v2x_regime) 
```

@@

```{r}
nelda2.sub <- nelda2.sub %>% filter(election_mdy >= "1989-10-04")
nelda2.sub <- nelda2.sub %>% filter(election_mdy <= "2013-01-13")
```

@@

nelda2.sub <- nelda2.sub %>% mutate(antigov.violence = ifelse(is.na(antigov.violence)==T, 0, antigov.violence))
nelda2.sub <- nelda2.sub %>% mutate(antigov.violence = ifelse(is.na(progov.violence)==T, 0, progov.violence))

nelda2.sub <- nelda2.sub %>% mutate(n.events.post = ifelse(is.na(n.events.post)==T, 0, n.events.post))
nelda2.sub <- nelda2.sub %>% mutate(d.events.num = ifelse(is.na(d.events.num)==T, 0, d.events.num))
#nelda2.sub <- nelda2.sub %>% mutate(median.participants = ifelse(is.na(median.participants)==T, 0, median.participants))

@@

##Making the assumption that NAs for pre-election protest are zero
nelda2.sub <- nelda2.sub %>% mutate(n.events.pre = ifelse(is.na(n.events.pre) == T, 0, n.events.pre))
nelda2.sub <- nelda2.sub %>% mutate(antigov.violence.pre = ifelse(is.na(antigov.violence.pre) == T, 0, antigov.violence.pre))
nelda2.sub <- nelda2.sub %>% mutate(progov.violence.pre = ifelse(is.na(progov.violence.pre) == T, 0, antigov.violence.pre))

@@

nelda2.sub <- nelda2.sub %>% mutate(n.events.post = ifelse(is.na(n.events.post) == T, 0, n.events.post))
nelda2.sub <- nelda2.sub %>% mutate(antigov.violence = ifelse(is.na(antigov.violence) == T, 0, antigov.violence))
nelda2.sub <- nelda2.sub %>% mutate(progov.violence = ifelse(is.na(progov.violence) == T, 0, progov.violence))

@@

 - Quick growth after fraud indicates opp believes state is weak
 - Slow or no growth after fraud indicates opp believes state is strong
 - Quick decay after peak indicates state is strong / believed strong (or not--regime is weak and so quickly collapses)
 - Slow decay after peak indicates state is weak / believed weak

@@

## Remove things other than protests
ecav_prot <- ecav %>% filter(str_detect(EventName, "rotest") == T | str_detect(EventName, "ccupation") == T |
                                  str_detect(EventName, "lockade") == T) #Only captures protests
```

Replacing NA protest size with average for that wave
```{r}
## Set up holding df

dv_df <- data.frame(NeldaID = NA, avg_size = NA)

## Filter by election and replace -99 with NA for protest size

 election_ids <- unique(ecav_prot$NeldaID)
ecav_prot <- ecav_prot %>% mutate(ParticipantNumber = ifelse(ParticipantNumber == -99, NA, ParticipantNumber))

for(i in 1:length(election_ids)){ 
  ecav_temp <- ecav_prot %>% filter(NeldaID == election_ids[i])  #There is a loop here

    ## Remove protests before election
  ecav_temp <- ecav_temp %>% filter(Date >= Electiondate)
  if(nrow(ecav_temp) == 0){
     new_row <- data.frame(NeldaID = election_ids[i], 
                           avg_size = 0) #No post-election protest

  dv_df[i,] <- new_row
  print(paste0("No post-election protest for observation ", i, "."))
  next
  } else{

  new_row <- data.frame(NeldaID = election_ids[i], avg_size = floor(mean(ecav_temp$ParticipantNumber, na.rm = T)))

  dv_df[i,] <- new_row
  print(paste0("Average size for observation ", i, " completed."))
  }
}

ecav_prot <- ecav_prot %>% left_join(dv_df, by = "NeldaID")

Current to-do: Double-check the output of the size code

```{r}
## Set up holding df

dv_df <- data.frame(NeldaID = NA, prot_intensity = NA, decay_intensity = NA, max_size = NA, day_max = NA)

ecav_prot <- ecav_prot %>% mutate(ParticipantNumber_adj = ifelse(is.na(ParticipantNumber)==T, avg_size, ParticipantNumber))
ecav_prot <- ecav_prot %>% mutate(ParticipantNumber_adj = ifelse(ParticipantNumber_adj == "NaN", 2, ParticipantNumber_adj)) #Assume NA size defaults to category 2

#ecav_rus <- ecav %>% filter(country == "Russia")   # Filter by country
ecav_prot <- ecav_prot %>% mutate(ParticipantNumber_num_min = ifelse(ParticipantNumber_adj == 1, 5, 
                                ifelse(ParticipantNumber_adj == 2, 55, 
                                       ifelse(ParticipantNumber_adj == 3, 550, 
                                              ifelse(ParticipantNumber_adj == 4, 5500,
                                                     ifelse(ParticipantNumber_adj == 5, 10000, NA))))))

@@

 election_ids <- unique(ecav_prot$NeldaID)

for(i in 1:length(election_ids)){ 
  ecav_temp <- ecav_prot %>% filter(NeldaID == election_ids[i])  #There is a loop here

@@

 ecav_temp_comb <- ecav_temp_comb %>% filter(date_col >= election_date_temp)

  if (nrow(ecav_temp_comb) == 0) {
    new_row <- data.frame(election_ids[i], NA, NA, NA, NA)
    dv_df[i,] <- new_row
    print(paste0("No post-election protests for obseveration ", i, ", election ID", election_ids[i], ","))
    next}  #End loop if zero post-election protests

@@

  # Assign NA to NA size
 if (nrow(max_data)==0){
    new_row <- data.frame(election_ids[i], NA, NA, NA, NA)
    dv_df[i,] <- new_row
    print(paste0("Election observation ", i, " completed. (Note: no size estimate."))
    next
 }

  if (nrow(max_data) >= 1) {
    prot_intensity <- max_data$total[1] / (1 + as.numeric(ymd(max_data$date_col[1]) - ymd(election_date_temp))) #[1] gets the first peak
    last_peak <- tail(max_data, n = 1)
    decay_intensity <-  last_peak$total / (1 + as.numeric(max(ecav_temp_comb$date_col) - (ymd(last_peak$date_col))))
    day_max <- as.numeric(ymd(max_data$date_col[1]) - ymd(election_date_temp))
    new_row <- data.frame(election_ids[i], prot_intensity, decay_intensity, max_data$total[1], day_max)
  new_row <- new_row %>% rename(max_size = max_data.total.1.)
    dv_df[i,] <- new_row
    print(paste0("Election observation ", i, " completed. (Note: multiple peaks."))
    next
  }

@@

  day_max <- as.numeric(ymd(max_data$date_col[1])) - as.numeric(ymd(election_date_temp))
  new_row <- data.frame(election_ids[i], prot_intensity, decay_intensity, max_data$total, day_max)
  new_row <- new_row %>% rename(max_size = max_data.total)

  dv_df[i,] <- new_row
  print(paste0("Election observation ", i, " completed."))

@@

```  
Pick up here with fixing this code:

```{r, eval=FALSE}
dv_df <- data.frame(NeldaID = NA, growth_coef = NA)
for(i in 1:length(election_ids)){
 ecav_temp <- ecav_prot %>% filter(NeldaID == election_ids[i])  #There is a loop here

###Getting a regression slope for protest size and time
  ecav_temp_comb <- ecav_temp %>% mutate(date_col = date(Date)) %>%
    group_by(date_col) %>%
     summarize(total = sum(ParticipantNumber_num_min))
  max_date_reg <- ecav_temp_comb %>% filter(total == max(total)) %>%  
   dplyr::select(date_col)

 ecav_temp_reg <- ecav_temp %>% filter(as_date(Date) >= as_date(Electiondate))
 ecav_temp_reg <- ecav_temp_reg %>% mutate(date_col = date(Date))
 ecav_temp_reg <- ecav_temp_reg %>% left_join(ecav_temp_comb, by = "date_col")  #Gets totals by date

 ecav_temp_reg <- ecav_temp_reg %>% filter(as_date(Date) <= max_date_reg[1,1])
 ecav_temp_reg <- ecav_temp_reg %>% mutate(date_index = as.numeric(ymd(ecav_temp_reg$Date) - ymd(Electiondate)))
 if(nrow(ecav_temp_reg) == 0) {
   new_row <- data.frame(election_ids[i], NA)
   dv_df[i,] <- new_row
   print(paste0("No observations for election number ", i, "."))
   next
 }
 if(length(unique(ecav_temp_reg$Date))==1){
   growth_coef <-  ((ecav_temp_reg$total - 0 )/((ecav_temp_reg$date_index+1)-0))[1] #m = (y2 - y1)/(x2 - x1) #+1 in denominator is a kludge to avoid Inf values for day 0 protests
   new_row <- data.frame(election_ids[i], growth_coef)
   dv_df[i,] <- new_row
   print(paste0("One date observed for election ", i, "."))
   next
 } else {

 fit <- lm(total ~ 0 + date_index, ecav_temp_reg)
 sum_table <- summary(fit)
 growth_coef <- sum_table$coefficients[1]
  new_row <- data.frame(election_ids[i], growth_coef)
   dv_df[i,] <- new_row
   print(paste0("Coefficient estimated for election ", i, "."))
 }
 rm(growth_coef)
}

nelda2.sub.b <- nelda2.sub.b %>% left_join( dv_df, by = "NeldaID")
```

```{r}
### Getting a regression slope for protest decay over time
# last_date_reg <- ecav_temp_reg %>% filter(Date == max(Date)) %>% slice_head(n=1) %>%
#   dplyr::select(Date)
# ecav_temp_reg_decay <- ecav_temp_reg %>% filter(Date >= as_date(max_date_reg$date_col))
#  ecav_temp_reg_decay <- ecav_temp_reg_deacy %>% mutate(date_index_decay = as.numeric(as_date(ecav_temp_reg_decay$Date) - as_date(max_date_reg$date_col)))
#  if(length(unique(ecav_temp_reg_deacy$Date)) == 1){
#    decay_coef <-  ((0-ecav_temp_reg_decay$total)/(1-0))[1] #m = (y2 - y1)/(x2 - x1) =
#  } else{
#    fit_decay <- lm(total ~ 0 + date_index_decay, ecav_temp_reg_decay)
# sum_table_decay <- summary(fit_decay)
# decay_coef <- sum_table_decay$coefficients[1]
#  }
#}

@@

## Coding for prior successful protest in political region

```{r}
success_cases <- nelda2.sub.b %>% filter(inc.replaced.prot == 1 | nelda35 == "yes") %>% dplyr::select(e_regionpol, year, election_mdy)

## Coding rule here: A successful protest counts in its region for 1 year after the election which sparked it; the wave ends 1 year after the last successful protest in a chain

nelda2.sub.b <- nelda2.sub.b %>% mutate(regional_success_lag = ifelse(e_regionpol == 1 & (election_mdy %within% interval(start = "1990-06-17", end = "1991-06-17") | election_mdy %within% interval(start = "2000-09-24", end = "2001-09-24") | election_mdy %within% interval(start = "2003-11-02", end = "2006-11-06")), 1, 
                                      ifelse(e_regionpol == 4 & (election_mdy %within% interval(start = "1997-04-13", end = "1998-04-13") | election_mdy %within% interval(start = "1998-05-23", end = "1999-05-23") | election_mdy %within% interval(start = "2000-10-22", end = "2001-10-22") | election_mdy %within% interval(start = "2007-07-22", end = "2008-07-22") | election_mdy %within% interval(start = "2010-11-28", end = "2011-11-28")), 1, 
                                             ifelse(e_regionpol == 2 & (election_mdy %within% interval(start = "2000-04-09", end = "2001-04-09") | election_mdy %within% interval(start = "2000-05-28", end = "2001-05-28") | election_mdy %within% interval(start = "2006-02-07", end = "2007-02-07")), 1, 
                                                    ifelse(e_regionpol == 8 & (election_mdy %within% interval(start = "1989-11-22", end = "1990-11-22")  | election_mdy %within% interval(start = "1996-02-15", end = "1997-02-15")), 1, 0)))))
```

@@

```{r}
write.csv(nelda2.sub.b, here::here("Data", "nelda2_sub_2023-05-30.csv"))
```

## Adding ERT data for regime duration

```{r, eval=FALSE}
nelda2.sub <- read.csv(here::here("Data", "nelda2_sub_2023-05-10.csv"))
ert <- read.csv(here::here("Data", "ert.csv"))
ert <- ert %>% filter(year > 1988)
ert.sub <- ert %>% dplyr::select(year, country_id, country_name, reg_start_year)
ert.sub <- ert.sub %>% mutate(country_id_year = paste(country_id, year, sep = "_"))

## ID numbers are the same because they both use V-dem format

ert.sub <- ert.sub %>% dplyr::select(country_id_year, reg_start_year)

nelda2.sub <- nelda2.sub %>% left_join(ert.sub, by = "country_id_year")

## Getting age of regime

nelda2.sub  <- nelda2.sub %>% mutate(regime_age = year - reg_start_year)

write.csv(nelda2.sub, here::here("Data", "nelda2_sub_2023-05-30.csv"))
